Check mixfdr in low noise simulation

### 2016-10-22 analysis/check_mixfdr_lownoise.Rmd
Revised check_mixfdr_lownoise.Rmd---not much to do there.

First simulate bimodal data with well-separated peaks. The histogram
shows the multi-modal nature of the underlying g is clear.
```{r}
  source("../code/dsc-shrink/datamakers/datamaker.R")
  sim.bimodal=rnormmix_datamaker(
              args=list(g=normalmix(c(0.5,0.5),c(-5,5),c(1,1)),
              min_pi0=0.4,
              max_pi0=0.4,
              nsamp=1000,
              betahatsd=1)
            )
  hist(sim.bimodal$input$betahat,nclass=20,xlim=c(-10,10),prob=TRUE,main="histogram of simulated betahat values")
```

Now run mixfdr on it. Note that the fit captures the multi-modal nature of g, 
although mixfdr continues to overestimate pi0.
```{r}
  source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
  sim.bimodal.mixfdroutput = mixfdr.wrapper(sim.bimodal$input,args=list(theonull=TRUE))
  g = mixfdr2fitted.g(sim.bimodal.mixfdroutput)$fitted.g
  x=seq(-10,10,length=100)
  plot(ecdf(sim.bimodal$meta$beta),main="Cdf of true beta: empirical (black) and fitted (red)")
  lines(x,mixcdf(g,x),col=2)
```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
source("chunk-options.R")
```

Simulate bimodal data with well-separated peaks. The histogram shows the
multi-modal nature of the underlying g is clear.

```{r sim_data}
source("../code/dsc-shrink/datamakers/datamaker.R")
sim.bimodal =
  rnormmix_datamaker(args = list(g = normalmix(c(0.5,0.5),c(-5,5),c(1,1)),
                                 min_pi0   = 0.4,
                                 max_pi0   = 0.4,
                                 nsamp     = 1000,
                                 betahatsd = 1))
hist(sim.bimodal$input$betahat,nclass = 20,xlim = c(-10,10),prob = TRUE,
     main="histogram of simulated betahat values")
```

Now run mixfdr on the simulated data. Note that the fit captures the
multi-modal nature of g, although mixfdr continues to overestimate pi0.

```{r fit_models}
source("../code/dsc-shrink/methods/mixfdr.wrapper.R")
sim.bimodal.mixfdroutput =
  mixfdr.wrapper(sim.bimodal$input,args = list(theonull = TRUE))
g = mixfdr2fitted.g(sim.bimodal.mixfdroutput)$fitted.g
x = seq(-10,10,length = 100)
par(cex.main = 1,font.main = 1)
plot(ecdf(sim.bimodal$meta$beta),cex = 0.6,
     main = "CDF of true beta: empirical (black) and fitted (red)")
lines(x,mixcdf(g,x),lwd = 2,lty = "dotted",col = "orangered")
```
